Interpretable Machine Learning

### 2017-11-30 talk.Rmd
fix one slide

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task)
```
## Step 3: Profit. We are done! {.center}

>>>>

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
library('mlr')
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task)
```
## Step 3: Profit. We are done! {.center}
